---
title: "Homework 5"
author: "Alyssa Monda"
date: "3/10/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## From Instructions

```{r}
library(car)
data(Wong)
library(dplyr)
# add an age group variable
Wong$agegrp <- case_when(
  (Wong$age > 0 & Wong$age <= 10) ~ 1,
  (Wong$age > 10 & Wong$age <= 20) ~ 2,
  (Wong$age > 20 & Wong$age <= 30) ~ 3,
  (Wong$age > 30 & Wong$age <= 40) ~ 4,
  (Wong$age > 40 & Wong$age <= 50) ~ 5,
  (Wong$age > 50 & Wong$age <= 60) ~ 6,
  (Wong$age > 60 & Wong$age <= 70) ~ 7,
  (Wong$age > 70 & Wong$age <= 100) ~ 8)

# convert to factor, add code levels and labels
Wong$agegrp <- factor(Wong$agegrp,
                  levels = c(1,2,3,4,5,6,7,8),
                  labels = c("Ages 1-10",
                             "Ages 11-10",
                             "Ages 21-10",
                             "Ages 31-10",
                             "Ages 41-10",
                             "Ages 51-10",
                             "Ages 61-70",
                             "Ages 71-100"))

```

## 1
Make a table of non-parametric statistics (median and IQR) for the number of days and duration grouped by `sex`. You'll be using `summarise()` from the `dplyr` package. For a given variable `x` you'll use `median(x, na.rm=TRUE)`, `quantile(x, 0.25, na.rm=TRUE)`, and `quantile(x, 0.75, na.rm=TRUE)`. Give the table a title using the `caption=` option and update the column names with something nice using the `col.names=` option in the `knitr::kable()` command. 

```{r}

```


##2
Make a table of parametric statistics (mean and SD) for the performance outcomes `piq` and `viq` grouped by `sex`. Like the table above, you'll be using `summarise()` from the `dplyr` package. Now you'll use `mean(x, na.rm=TRUE)` and `sd(x, na.rm=TRUE)`. Give the table a title using the `caption=` option and update the column names with something nice using the `col.names=` option in the `knitr::kable()` command.

```{r}

```


##3
Make a table containing the frequencies and relative percentages for `agegrp`. Use the example we did in class to help guide you.

```{r}

```

##4
Make a regression model (Model 1) for the performance IQ (`piq`) using `age` and `sex`. Put the regression model results into a table.

```{r}

```
 
##5
Make a second regression model (Model 2) for performance IQ (`piq`) using `age` and `sex` plus `days` and `duration`. Put the regression model results into a table.

```{r}

```

##6
Finally, make a table showing the results from the `anova()` command comparing Model 1 and Model 2 you made above using the example we did in class as a guide. 

```{r}

```


##7
STUDENT CHOICE - pick either a `htmlwidget` from [http://gallery.htmlwidgets.org/](http://gallery.htmlwidgets.org/) or do a "flexdashboard" using the templates at [http://rmarkdown.rstudio.com/flexdashboard/](http://rmarkdown.rstudio.com/flexdashboard/) as a guide.

```{r}

```


## References
Wong, P. P., Monette, G., and Weiner, N. I. (2001) Mathematical models of cognitive recovery. Brain Injury, 15, 519–530.

Fox, J. (2016) Applied Regression Analysis and Generalized Linear Models, Third Edition. Sage.